A fully labelled proof system for intuitionistic modal logics

### 2019-10-03 caleidoscope/soundness.tex
adding some cases to soundness section

\begin{proof}
	We proceed by induction on the height of the derivation of $\SG$, and we show for all rules in $\labIKp$
	$$
	\vliiinf{\labrn{r}}{}{\SG}{\SGi1}{\cdots}{\SGi n}
	$$ for $n\in\{0,1,2\}$, that whenever $\SGi1,\ldots,\SGi n$ are
	valid in all birelational frame, then so is $\SG$. It follows a case analysis on $\rn r$:
	\begin{itemize}
		\item $\rlabrn\bot$: This is trivial because $\bot$ is never forced.
		\item $\rn{id}$: This follows immediately from Proposition~\ref{prop:mon}.
		\item $\llabrn\BOX$: By way of contradiction, assume $\B, \Left,
		\futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
		is valid in all birelational frames, but $\B,\Left, \futs xy,
		\accs yz, \labels{x}{\BOX A} \SEQ \Right$ is not. This means that
		we have a model $\M$ and an interpretation $\inter\cdot$, such
		that $\M,\inter\cdot\not\Vdash\B,\Left, \futs xy, \accs yz,
		\labels{x}{\BOX A} \SEQ \Right$, i.e., $\inter x\le_\M\inter y$
		and $\inter y\rel_\M\inter z$ and $\cforce \M x{\BOX A}$ and
		$\cnforce \M wB$ for all $\labels wB\in\Right$. However, by the
		definition of forcing in~\eqref{eq:kripke} we also have $\cforce
		\M zA$, and consequently $\nforce \M{\inter\cdot}{\B, \Left, \futs
			xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
			\Right}$. Contradiction.
		\item $\rlabrn\BOX$: By way of contradiction, assume that $\futs xy,
		\accs yz, \Left \SEQ \Right, \labels{z}{A}$ is valid in all
		birelational frames, but $\B, \Left \SEQ \Right, \labels{x}{\BOX
			A}$ is not, where $\lb y$ and $\lb z$ do not occur in $\B$ or
		$\Left$ or $\Right$.This means that we have a model $\M$ and an
		interpretation $\inter\cdot$, such that
		$\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{\BOX
				A}}$. This means that there are worlds $\lb{y'}$ and $\lb{z'}$
		in $\M$ such that $\inter x\le_\M \lb{y'}$ and
		$\lb{y'}\rel_\M\lb{z'}$ and $\cforce\M{z'}{A}$. Now we let
		$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter
		y'=\lb{y'}$ and $\inter z'=\lb{z'}$ and $\inter\cdot'=\inter\cdot$
		on all other labels. Then $\nforce\M{\inter\cdot'}{\futs xy,
			\accs yz, \Left \SEQ \Right, \labels{z}{A}}$. Contradiction.
		\item \lutz{if you want, you can add some more cases here, following the pattern above.}
	\end{itemize}
	The other cases are similar (and simpler), and we leave them to the
	reader. In particular, note that the cases for the rules $\rn{refl}$,
	$\rn{trans}$, $\rn{F_1}$ and $\rn{F_2}$ are trivial, as all
	birelations frames have to obey the corresponding conditions.
\end{proof}

>>>>

\begin{proof}
	We proceed by induction on the height of the derivation of $\SG$, and we show for all rules in $\labIKp$
	$$
	\vliiinf{\labrn{r}}{}{\SG}{\SGi1}{\cdots}{\SGi n}
	$$ for $n\in\{0,1,2\}$, that whenever $\SGi1,\ldots,\SGi n$ are
	valid in all birelational frame, then so is $\SG$. It follows a case analysis on $\rn r$:
	\begin{itemize}
		\item $\rlabrn\bot$: This is trivial because $\bot$ is never forced.
		\item $\rn{id}$: This follows immediately from Proposition~\ref{prop:mon-adm}.
		\item $\llabrn\BOX$: By way of contradiction, assume that $\B, \Left,
		\futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
		is valid in all birelational frames, but $\B,\Left, \futs xy,
		\accs yz, \labels{x}{\BOX A} \SEQ \Right$ is not. This means that
		we have a model $\M$ and an interpretation $\inter\cdot$, such
		that $\M,\inter\cdot\not\Vdash\B,\Left, \futs xy, \accs yz,
		\labels{x}{\BOX A} \SEQ \Right$, i.e., $\inter x\le_\M\inter y$
		and $\inter y\rel_\M\inter z$ and $\cforce \M x{\BOX A}$ and
		$\cnforce \M wB$ for all $\labels wB\in\Right$. However, by the
		definition of forcing in~\eqref{eq:kripke} we also have $\cforce
		\M zA$, and consequently $\nforce \M{\inter\cdot}{\B, \Left, \futs
			xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
			\Right}$. Contradiction.
		\item $\rlabrn\BOX$: By way of contradiction, assume that $\B, \futs xy,
		\accs yz, \Left \SEQ \Right, \labels{z}{A}$ is valid in all
		birelational frames, but $\B, \Left \SEQ \Right, \labels{x}{\BOX
			A}$ is not, where $\lb y$ and $\lb z$ do not occur in $\B$ or
		$\Left$ or $\Right$.This means that we have a model $\M$ and an
		interpretation $\inter\cdot$, such that
		$\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{\BOX
				A}}$. This means that there are worlds $\lb{y'}$ and $\lb{z'}$
		in $\M$ such that $\inter x\le_\M \lb{y'}$ and
		$\lb{y'}\rel_\M\lb{z'}$ and $\nforce\M{\lb{z'}}{\fm A}$. Now we let
		$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter
		y'=\lb{y'}$ and $\inter z'=\lb{z'}$ and $\inter\cdot'=\inter\cdot$
		on all other labels. Then $\nforce\M{\inter\cdot'}{\B, \futs xy,
			\accs yz, \Left \SEQ \Right, \labels{z}{A}}$. Contradiction.

		\item $\rlabrn\IMP$: By way of contradiction, assume that $\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}$ is valid in all birelational frames, but $\B, \Left \SEQ \Right, \labels{x}{A \IMP B}$ is not, where $\lb y$ does not occur in $\B$ or $\Left$ or $\Right$. This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}$. This means that there exists world $\lb{y'}$ in $\M$ such that $\inter x\le_\M \lb{y'}$ and $\cforce\M{y'}{A}$ but $\nforce\M{\lb{y'}}{\fm B}$. Now we let 	$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot'=\inter\cdot$ on all other labels. Then $\nforce\M{\inter\cdot'}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$. Contradiction.

		\item $\llabrn\DIA$: By way of contradiction, assume that $\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$ is valid in all birelational frames, but $\B, \Left, \labels{x}{\DIA A} \SEQ \Right$ is not, where $\lb y$ does not occur in $\B$ or $\Left$ or $\Right$. This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}$, i.e. $\cforce \M x{\DIA A}$. This means that there exists world $\lb{y'}$ in $\M$ such that $\inter x\rel_\M \lb{y'}$ and $\cforce \M {\lb{y'}}{A}$. Now we let $\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot' = \inter\cdot$ on all other labels. Then $\nforce\M{\inter\cdot'}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$. Contradiction.

		%\item $\rlabrn\DIA$: By way of contradiction, assume that $\B, \accs xy, \Left \SEQ \Right,  \labels{x}{\DIA A}, \labels{y}{A}$ is valid in all birelational frames, but $\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$ is not. This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}$, i.e., $\inter x\rel_\M\inter y$ and $\nforce\M {\lb x}{\fm{\DIA A}}$. This means that for all worlds $\lb{y}$ where $\inter x\rel_\M\inter y$,  \marianela{to be completed}
	\end{itemize}
	The other cases are similar (and simpler), and we leave them to the
	reader. In particular, note that the cases for the rules $\rn{refl}$,
	$\rn{trans}$, $\rn{F_1}$ and $\rn{F_2}$ are trivial, as all
	birelations frames have to obey the corresponding conditions.
\end{proof}
